Synthesis of production rules for glycans

### 2020-10-16 papers/sugar-synth/experiments.tex
conflict changes

{\em Benchmark: }
We have applied our tool on four sets of molecules form
respiratory mucins of a cystic fibrosis patient (D1),
human chorionic gonadotropin from a cancer cell line (D2), horse chorionic gonadotropin (D3), and
hydra (D4)~\cite{Jaiman2018,hydra}.
The availability of clean data, where we are clear about the source and the collection
methodology used, limits our choices for the data.

@@

{\em Results:} We have applied \ourtool~on the data set. For each data set, we choose several
parameter combinations to illustrate the relative performance of the tool.
If we did not give large enough parameters, then the tool fails to synthesize the rules.

For D1, we synthesize the rules in 1.2 seconds. If we reduced any of the first
two parameters, we failed.
Giving an extra compartment in the first row did not impact the performance.
We synthesize the rules for D2, which is also our motivating example, in 0.4 seconds.
The performance of the tool is also robust against variations of the parameters.
We synthesize the rules for D3 in 0.9 seconds if we use optimal values for the parameter.
However, if we use too many resources or too little, the tool runs for a long time,
which is typical. The search in combinatorial space is highly sensitive to the parameters.

The synthesis for D4 takes a long time. We also observe the trade-off between the number of compartments
and the depth of the rules at the first and second row of D4.
For D3, we also learned large rules, i.e., they are adding many nodes at a single time.
Currently, the tool does not have any objective function to optimize the synthesized rules.
We are hoping to see more data sets such that we can develop a clearer picture
for a reasonable objective function.

@@

The results suggest that the tool is potentially applicable to larger data sets.
% with
% the variants discussed earlier.
% However, we have not fully modeled all the information
% and biological intuition --- for example, the objective function for the rules.

>>>>

{\em Benchmark: }
We have applied our tool on four sets of molecules form
respiratory mucins of a cystic fibrosis patient (D1),
horse chorionic gonadotropin (D2),
SARS-COV-2 (D3),
human chorionic gonadotropin from a cancer cell line (D4),
and
synthetic data (D5)~\cite{Jaiman2018,SarsCov2}.
The availability of clean data, where we are clear about the source and the collection
methodology used, limits our choices.

@@

{\em Results:} We have applied \ourtool~on the data set. For each data set, we choose several
parameter combinations to illustrate the relative performance of the tool.
If we did not budget large enough parameters, then the tool fails to
synthesize the rules.
We present the rules learned after giving minimum resources.
Our tool gave output that matched with the analysis of~\cite{Jaiman2018}
in reasonable time.

Currently, the tool does not have any objective function to optimize the synthesized rules.
We are hoping to see more data sets such that we can develop a clearer picture
for a reasonable objective function.
The results suggest that the tool is potentially applicable to larger data sets.

% For D1, we synthesize the rules in 1.2 seconds. If we reduced any of the first
% two parameters, we failed.
% Giving an extra compartment in the first row did not impact the performance.
% We synthesize the rules for D2, which is also our motivating example, in 0.4 seconds.
% The performance of the tool is also robust against variations of the parameters.
% We synthesize the rules for D3 in 0.9 seconds if we use optimal values for the parameter.
% However, if we use too many resources or too little, the tool runs for a long time,
% which is typical. The search in combinatorial space is highly sensitive to the parameters.

% The synthesis for D4 takes a long time. We also observe the trade-off between the number of compartments
% and the depth of the rules at the first and second row of D4.
% For D3, we also learned large rules, i.e., they are adding many nodes at a single time.
% %

@@

% with
% the variants discussed earlier.
% However, we have not fully modeled all the information
% and biological intuition --- for example, the objective function for the rules.
